Radio Telescope Observations Of The April 8, 2024 Total Solar Eclipse At 1420MHz.

### 2025-03-01 sections/theoretical.tex
Changed Theoretical Section slightly, adding a little groundwork for when we add more figures.

Using these relationships, we can create theoretical lightcurves for varying solar radii.
We calculated the obscured area of the solar disk at 2000 points in time during the eclipse.
Our data found that the radio lightcurve reached a minimum of 30.9\% of the total solar flux during totality, whereas the optical lightcurve reached 0\%.
Assuming a uniform disk brightness, we created theoretical lightcurves for solar radii ranging from $R = 1.0 R_{\odot}$ to $R = 1.5 R_{\odot}$.
These theoretical lightcurves, shown in Figure \ref{fig:TheoreticalVsRadio}, helped us match the dip in relative difference in brightness within the radio lightcurve.
Our model does not take into acount the true non-uniformity of the solar surface, nor does it account for limb darkening.
We found that the best-fit curve has an apparent solar radius of $R_{\mathrm{1420}} = 1.27 R_{\odot}$.

>>>>

Using these relationships, we can create theoretical lightcurves for varying solar radii.
We calculated the obscured area of the solar disk at 2000 points in time during the eclipse.
Our data found that the radio lightcurve reached a minimum of 30.9\% of the total solar flux during totality, whereas the optical lightcurve reached 0\%.
Assuming a uniform disk brightness, we created theoretical lightcurves for solar radii ranging from $R = 1.0 R_{\odot}$ to $R = 1.5 R_{\odot}$.
These theoretical lightcurves, shown in Figure \ref{fig:RadiovsTheoretical}, helped us match the dip in relative difference in brightness within the radio lightcurve.
Our model does not take into acount the true non-uniformity of the solar surface, nor does it account for limb darkening.
We found that the best-fit curve has an apparent solar radius of $R_{\mathrm{1420}} = 1.27 R_{\odot}$.
